Literature review of Formal Methods applied to Blockchain technology

### 2022-01-09 article/article.tex
add software quality book ref, modelling section

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  A clear and well-documented \LaTeX\ document is presented as an
  article formatted for publication by ACM in a conference proceedings
  or journal publication. Based on the ``acmart'' document class, this
  article presents and explains many of the common variations, as well
  as many of the formatting elements an author may use in the
  preparation of the documentation of their work.
\end{abstract}

@@

\section{Introduction}
ACM's consolidated article template, introduced in 2017, provides a
consistent \LaTeX\ style for use across ACM publications, and
incorporates accessibility and metadata-extraction functionality
necessary for future Digital Library endeavors. Numerous ACM and
SIG-specific \LaTeX\ templates have been examined, and their unique
features incorporated into this single new template.

If you are new to publishing with ACM, this document is a valuable
guide to the process of preparing your work for publication. If you
have published with ACM before, this document provides insight and
instruction into more recent changes to the article template.

The ``\verb|acmart|'' document class can be used to prepare articles
for any ACM publication --- conference or journal, and for any stage
of publication, from review to final ``camera-ready'' copy, to the
author's own version, with {\itshape very} few changes to the source.

@@

\section{Acknowledgments}

Identification of funding sources and other support, and thanks to
individuals and groups that assisted in the research and the
preparation of the work should be included in an acknowledgment
section, which is placed just before the reference section in your
document.

This section has a special environment:
\begin{verbatim}
  \begin{acks}
  ...
  \end{acks}
\end{verbatim}
so that the information contained therein can be more easily collected
during the article metadata extraction phase, and to ensure
consistency in the spelling of the section heading.

Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

\section{Appendices}

If your work needs an appendix, add it before the
``\verb|\end{document}|'' command at the conclusion of your source
document.

Start the appendix with the ``\verb|appendix|'' command:
\begin{verbatim}
  \appendix
\end{verbatim}
and note that in the appendix, sections are lettered, not
numbered. This document has two appendices, demonstrating the section
and subsection identification method.

\section{SIGCHI Extended Abstracts}

The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
not in Word) produces a landscape-orientation formatted article, with
a wide left margin. Three environments are available for use with the
``\verb|sigchi-a|'' template style, and produce formatted output in
the margin:
\begin{itemize}
  \item {\verb|sidebar|}:  Place formatted text in the margin.
  \item {\verb|marginfigure|}: Place a figure in the margin.
  \item {\verb|margintable|}: Place a table in the margin.
\end{itemize}

%%
%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
  To Robert, for the bagels and explaining CMYK and color spaces.
\end{acks}

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  Lorem ipsum dolor sit amet, consectetur adipiscing elit. 
  Vestibulum enim nibh, aliquet sit amet ex suscipit, efficitur fringilla enim. 
  Vestibulum elementum fringilla sodales. Cras malesuada sollicitudin consectetur.
  Cras elit nibh, tempus elementum dui vitae, sagittis porttitor elit. In sollicitudin purus neque, eu tristique felis varius in. Morbi sed commodo eros.
  Pellentesque ornare sed felis et bibendum.
\end{abstract}

@@

\section{Introduction}
The rising complexity of features offered by software gives us the ability to use it for the most integrity and reliability dependent needs of our lives. 
Information systems that rely on these base principles can be financial and health related services, and in most recent times, blockchain based applications. 
Blockchain, being a decentralized and distributed network protocol that can be used as the core of a monetary system that performs peer-to-peer transactions, 
it needs the assurance of coordination and consensus of its economy’s state~\cite{Duan2018}. 
Knowing that the protocol of a given blockchain project is what dictates how transactions and their coordination is maintained, the assurance of security and safety is a given. 
Formal methods can be introduced in order to provide unequivocal evidence that a given blockchain system and its consensus algorithm are secure and in according to expected software quality.

Formal methods are a rigorous description of a system or process using mathematics that aims to provide evidence of its reliability and robustness, 
according the specification in question~\cite{Regan2014}.

//TODO FINISH

\section{Formal Modeling Application}
Blockchain systems can be divided into five main layers~\cite{Duan2018}: Blockchain system, Consensus, Smartcontract and Application. 
As seen on Figure~\ref{fig:blockchain-layers}.

\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{blockchain-layers}
  \caption{Blockchain infrastructure, from \cite{Duan2018}}
  \Description{Ilustration of the layers that describe a blockchain system}
  \label{fig:blockchain-layers}
\end{figure}

@@
